---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: Arial, sans-serif;
  margin: 20px;
}

h2 {
  color: #333333;
}

p {
  font-size: 16px;
  line-height: 1.5;
}
```
## Campus Drink Observations

This dynamic report presents observational data on café-style drinks carried by people on campus. Each row represents one observation. The aim is to identify patterns in drink type, drink temperature, and the number of people carrying drinks.

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTjwOnsN_H0_VqjDTOfpu_-yEf_WJE3MCGNoaHukTPr7QHzzQxdUY29SoyEgweARQZs1WYMOWmsnrxa/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    drink_type = `What type of drink was observed?`,
    drink_temp = `Was the drink hot or cold?`,
    number_carrying = `How many people in the observed group were carrying a drink?`,
    location = `Where was the observation made?`,
    time_of_day = `What time of day was the observation made?`
  )

mean_people <- latest_data %>%
  summarise(mean_people = mean(number_carrying, na.rm = TRUE)) %>%
  pull(mean_people)

max_people <- latest_data %>%
  summarise(max_people = max(number_carrying, na.rm = TRUE)) %>%
  pull(max_people)

```

The average number of people carrying drinks per observation is `r round(mean_people, 2)`.

The maximum number of people carrying drinks observed was `r max_people`.

The bar charts below show the distribution of drink types and drink temperatures across the observations.

```{r}
ggplot(latest_data, aes(x = drink_type)) +
  geom_bar() +
  labs(
    title = "Observed drink types on campus",
    x = "Drink type",
    y = "Count"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
```{r}
ggplot(latest_data, aes(x = drink_temp)) +
  geom_bar() +
  labs(
    title = "Hot vs cold drinks observed",
    x = "Drink temperature",
    y = "Count"
  ) +
  theme_minimal()

```